Merra2

### 2020-07-16 Rcode/Merra2.Rmd
final

New data mean in Parks
```{r}
require(exactextractr)

#Get Merra2 files

@@

for (i in c(1980,2004)){ #this will have all the years whe we actually do it. The example folder only has 1980 and 2004
  for (j in c("01","10")){ #same as above but for months
    x<-(paste0(i,j))
  assign(paste0("x",i,j),fileNames[grep(x,fileNames)])
  }}

#fix - may not have to do this now
# x198001<-paste0("/Users/killion/Documents/GitHub/SmokeProject/MERRA_DATA_ORG_PRACT/",x198001) #need full filepath - can you add in loop above??
# x200410<-paste0("/Users/killion/Documents/GitHub/SmokeProject/MERRA_DATA_ORG_PRACT/",x200410)

list_all<- list(x198001,x200410) #will need to output all lists above in for loop into another list

#the "level" dimension refers to veritcal layers where 72=surface and 1=top of atmosphere
#for a single day
empty_list<-list()

for (i in 1:length (list_all)) {
    for (j in 1:length (list_all[[i]])){
 bcphilic<-mean(brick(list_all[[i]][[j]], varname="BCPHILIC", level=72)) #one day - first bracket is month, 2nd is day, within a day is 8 layers by hour
bcphobic<-mean(brick(list_all[[i]][[j]], varname="BCPHOBIC", level=72))
ocphilic<-mean(brick(list_all[[i]][[j]], varname="OCPHILIC", level=72))
ocphobic<-mean(brick(list_all[[i]][[j]], varname="OCPHOBIC", level=72))

@@

#Make list of all objects - assign(paste0(“day”,j), <- exact_extract(all, poly, 'mean') - 
empty_list[[j]]<-exact_extract(all, poly, 'mean') #intersects boundary

    }
  #take mean of the assign list above

out<-as.data.frame(empty_list)
out_mean<-as.data.frame(rowMeans(out))

#write csv
  n<-substr(list_all[[i]][[j]],94,100) # !!!!!!!! you will have to change this based on the length of your filepaths
  colnames(out_mean)[1] <- n #give values column name based on month
   name<-paste0("/Users/killion/output_means/",n) #create empty folder to save to
    newname<-paste0(name, ".csv")
write.csv(out_mean, newname, row.names = FALSE) #save as csv

@@

#save
write.csv(final_means, "/Users/killion/final_means.csv", row.names = FALSE)

>>>>

New data mean in Parks
```{r}

poly<-sf::st_as_sfc(nps) #converts to new type of poly

@@

years<-c(1980,2004)  #all the years
months<-c("01","10") #all the months
comb<-expand.grid(years,months) #just to get the number of unique combinations
list_all<-list() #create an empty list to fill with the file names

for (i in 1:nrow(comb)){ #creates the number of list objects
  year<-comb[i,]$Var1
  month<-comb[i,]$Var2
      x<-(paste0(year,month))
      list_all[[i]]<-fileNames[grep(x,fileNames)]  #fill the list with the file names
      names(list_all)[i]<-paste0("x",year,month) #name the list objects
}

# list_all<- list_all[c(1,4)] You will need to use this with our sample data folder

empty_list<-list()

for (i in 1:length (list_all)) {
    for (j in 1:length (list_all[[i]])){
 bcphilic<-mean(brick(list_all[[i]][[j]], varname="BCPHILIC", level=72)) #one day - first bracket is month, 2nd is day, within a day is 8 layers by hour - the "level" dimension refers to veritcal layers where 72=surface and 1=top of atmosphere
bcphobic<-mean(brick(list_all[[i]][[j]], varname="BCPHOBIC", level=72))
ocphilic<-mean(brick(list_all[[i]][[j]], varname="OCPHILIC", level=72))
ocphobic<-mean(brick(list_all[[i]][[j]], varname="OCPHOBIC", level=72))

@@

empty_list[[j]]<-exact_extract(all, poly, 'mean') #intersects boundary

out<-as.data.frame(empty_list)
out_mean<-as.data.frame(rowMeans(out)) #take mean of the assign list above

#write csv
  n<-substr(list_all[[i]][[j]],94,100) # !!!!!!!! you will have to change 94 and 100 based on the length of your filepaths - this selects just the year and month i.e. 20041008
  colnames(out_mean)[1] <- n #give values column name based on month
   name<-paste0("/Users/killion/output_means/",n) #create empty folder to save to
    newname<-paste0(name, ".csv")
write.csv(out_mean, newname, row.names = FALSE) #save as csv

@@

#save
write.csv(final_means, "/Users/killion/final_means2.csv", row.names = FALSE)
